---
name: Dr. J Michael
surname: Johnson
position: 'Data Scientist | Geographer | Water Resources'
address: Fort Collins, Colorado
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD
googlescholar: MrXM9cgAAAAJ
email: 'jjohnson@lynker.com'
www: mikejohnson51.github.io
github: mikejohnson51
fontawesome: yes
docname: Curriculum Vitae
aboutme: I am a \textcolor{cyan}{\textbf{water resource data scientist}} leading the \textcolor{cyan}{\textbf{hydrofabric development for NOAA's Next Generation National Water Model}} along with collaborative federal efforts to define a national suite of hydroinformatic data products. I seek to bridge \textcolor{cyan}{\textbf{data-intensive computational geography}} with \textcolor{cyan}{\textbf{water resources research}} and develop open-source software to ease community access to big data and design new data products.
headcolor: 414141
csl: apa-cv.csl
output: 
  vitae::awesomecv:
    keep_tex: true
    pandoc_args: ["--lua-filter=lua/strong.lua"]
---

```{r setup, include=FALSE}
library(scholar)
library(vitae)
library(stringr)
library(readr)
library(RefManageR)
library(tidyr)
library(dplyr)
library(gsheet)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, error=FALSE)

gs_id = 'MrXM9cgAAAAJ'
mike_gs = get_profile(gs_id) 

cites = get_publications(gs_id) %>% 
   filter(!grepl("AGU|EGU|Fall Meeting", journal)) %>%
   filter(journal != "")

follow = readLines('https://img.shields.io/github/followers/mikejohnson51?label=follow&style=social')
f = str_match(follow, "<title>Follow: \\s*(.*?)\\s*</title>")[,2]

stars = readLines('https://img.shields.io/github/stars/mikejohnson51?affiliations=OWNER%2CCOLLABORATOR&style=social')
s = str_match(stars, "<title>Stars: \\s*(.*?)\\s*</title>")[,2]

funds = gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=0') 

personal = sum(ifelse(is.na(parse_number(funds$amount2)), parse_number(funds$amount), parse_number(funds$amount2)))
personal = paste0("$", formatC(as.numeric(personal), format="f", digits=0, big.mark=","))

team = sum(parse_number(funds$amount))
team = paste0("$", formatC(as.numeric(team), format="f", digits=0, big.mark=","))

```

# Employment

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data Scientist", "Lynker", "Fort Collins, Colorado", "August 2020 - Present", 
    list("Lead the spatial data development for the NOAA NextGen Water Resource Modeling Framework",
         "Contribute to local and state level consulting projects related to water resource managment and hazard mitigation",
         "Recruit, retain, and mentor a strong and diverse group of data scientists"
    ),
  
  "Hydrofabric Technical Director", "NOAA Office of Water Prediction", "Remote", "Sep 2022 - Present", 
    list("Develop the foundational geospatial data to support verson 4 of the National Water Model",
         "Collaborate with the USGS to build a suite of tools and data products supporting the National Hydrologic Geospatial Fabric", 
         "Lead a team developing novel Machine learning, geospaial, and cloud based solutions of more open and skilled science"),
  
  "Lead Data Scientist", "Urban Flooding Open Knowledge Network", "Remote", "Sep 2019 - Apr 2023", 
    list("Co-authored two successful proposals to NSF and acted as an advocate for the team in the initial C-ACCEL program",
      "Developed and designed a cost effective, cloud native, building level, flood forecasting system for the Continental United States."),
  
  "Lecturer", "Geography Department", "UC Santa Barbara", "2021", 
    list("Designed and taught the first programming based GIS course for UCSB in R."),
  
  "Course Coordinator", "NOAA Office of Water Prediction", "Tuscaloosa, AL", "2016", 
    list("Lead students towards the successful execution of projects related to the National Water Model
Research Fellow",
   "Worked at the National Water Center in advancement of the National Water Model"),
  
  "Graduate Student", "Visiting Researcher", "", "", 
    list("\\textbf{Institute for Environmental Studies}. Vrije Universiteit, Amsterdam: June - July 2019; January - March 2018", 
         "\\textbf{Research Applications Laboratory. NCAR}, Boulder, Colorado: August - September 2018",
         "\\textbf{NOAA National Water Center}. Tuscaloosa, Alabama: Summers of 2016.2017")

) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Geography", "University of California, Santa Barbara", "Santa Barbara, CA", "2021", 
    list("\\textbf{Advisor}: Dr. Keith C. Clarke",
         "\\textbf{Committee}: Hugo Loaiciga, Kelly Caylor, David Blodgett",
         "\\textbf{Title}: The Role of Spatial Data Science in Continental Scale Hydrology: Twelve Case Studies in Data Models, Data Structures, Modeling, and Evaluation"),

  "BS in Anthropology & Geography, Cum Laude", "California Polytechnic State University", "San Luis Obispo, CA", "2010 - 2015", 
    list("Recipient of the Outstanding Senior Award",
         "\\textbf{Minors}: \\textbf{(1)} GIS for Agriculture \\textbf{(2)} Water Science (Watershed Management) \\textbf{(3)} Statistics \\textbf{(4)} Economics \\textbf{(5)} Environmental Studies")
) %>% 
  detailed_entries(what = degree, 
                   when = dates, 
                   with = uni, 
                   where = loc, 
                   why = details)
```
\newpage

# Publications

\textcolor{cyan}{ \href{https://tinyurl.com/mike-google-scholar}{\faicon{google} Google Scholar: `r mike_gs$total_cites` citations; \faicon{user} `r length(mike_gs$coauthors)` collaborators; \faicon{file} `r nrow(cites)` papers} \newline
\textbf{h-index} `r mike_gs$h_index`; \textbf{i-index} `r mike_gs$i10_index`}

```{r}
data = cites  %>%
  mutate(bibtype = "article")
  # arrange(-year) %>%
  # mutate(author = gsub("J Johnson", "JM Johnson", author),
  #        author = gsub("JM Johnson", "JM Johnson", author),
  #        author = gsub("Johnson, J", "JM Johnson", author),
  #        author = gsub("Johnson, J. Michael", "JM Johnson", author),
  #        title  = gsub("Ogc", "OGC", title),
  #        #itle  = gsub("HY_Features", "HY Features", title),
  #        #title  = stringr::str_to_title(title),
  #
  #        journal  = stringr::str_to_title(journal),
  #        bibtype = "article")

  as.BibEntry(data) %>%
  WriteBib("mike-gs.bib")

bibliography_entries("mike-gs.bib") %>%
  arrange(desc(issued))

```

# Grants and Fellowships

\textcolor{cyan}{I have personally solicited \textbf{\`r personal`} for research and development and been a core member of teams who have solicited \textbf{\`r team`}.}

```{r}
funds %>%
  mutate(amount = ifelse(is.na(amount2) | amount2 == 0,
                         amount,
                         paste0(amount, " (Subaward: ", amount2, ")"))) %>% 
  detailed_entries(what  = source, 
                   when  = date,
                   with  = name, 
                   where = amount)
```

# Teaching experience

## University Teaching

```{r}
tribble(
  ~ class, ~ uni, ~ loc, ~ dates, ~ details,
  "Introduction to Geoinformatics", "University of California, Santa Barbara, California", "Santa Barbara, CA", "2021", 
    list("Independently developed and taught to address the growing need for data science in the GIS profession.",
         "Intended to become prerequisite course for the UCSB Geography Department and Masters in GIS Curriculum",
         "\\href{https://mikejohnson51.github.io/spds/}{Open course content available here}")) %>% 
  detailed_entries(what = uni, 
                   when = dates, 
                   with = class, 
                   where = loc, 
                   why = details)
```

## Teaching Assistant

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=1727236529') %>% 
  filter(type == "Teaching Assisstant")  %>%
  mutate(quarter = factor(quarter, levels = c("Fall", "Winter", "Spring", "Summer"), 
                          ordered = T),
         class_link = ifelse(is.na(link), class, 
                             paste0('<a href="',link, '">', class, '</a>'))) %>% 
  group_by(class) %>%
  mutate(points = as.numeric(year) + as.numeric(quarter)/10,
         professor = paste(unique(professor), collapse = ", ")) %>% 
  summarise(year = paste(year,collapse=', '), 
            points = max(points),
            professor = professor[1],
            division = division[1]) %>% 
  unite(data, year, sep = " ") %>% 
  arrange(desc(points)) %>% 
  detailed_entries(professor, division, class, data)
```

## Award Nominations

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=1280463790') %>% 
  group_by(name) %>% 
  mutate(year = paste(year, collapse=', ')) %>% 
  slice(1) %>% 
  select(-sort, -source) %>% 
  detailed_entries(when = year, with = name)
```
# Open Source Software

\textcolor{cyan}{\href{https://github.com/mikejohnson51}{\faicon{github} Github: \faicon{user} `r f` followers; \faicon{star} `r s` stars}}

```{r}
tribble(
  ~ pkg, ~ role, ~ details,
  "\\href{https://github.com/mikejohnson51/AOI}{AOI}", "Lead Developer", "Fast and flexible geocoding and AOI creation.",

  "\\href{https://github.com/mikejohnson51/climateR}{climateR}", "Lead developer", "Instant access to gridded and observation climate data.",

  "\\href{https://github.com/mikejohnson51/climateR-catalogs}{climateR-catalogs}", "Lead developer", "A consistent federated data catalog for programmatic access.",

  "\\href{https://github.com/mikejohnson51/zonal}{zonal}", "Lead developer", "Fast, flexable spatial data summarization.",

  "\\href{https://github.com/mikejohnson51/nwmTools}{nwmTools}",  "Lead developer", "National Water Model Streamflow access.",

  "\\href{https://github.com/doi-usgs/nhdplusTools}{DOI-USGS/nhdplusTools}",  "Author", "Manipulating hydrographic data with the NHDPlus data model.",

  "\\href{https://github.com/doi-usgs/dataRetrieval}{DOI-USGS/dataRetrieval}",  "Author", "R Interface to the USGS data holdings.",

  "\\href{https://github.com/doi-usg/hyRefactor}{DOI-USGS/hyRefactor}",  "Author", "Manipulating the NHDPlus Network for Hydrologic Modeling.",

  "\\href{https://github.com/NOAA-OWP/hydrofabricI}{NOAA-OWP/hydrofabric}", "Lead Developer", "Generating data products for continental scale hydrology",
) %>%
 detailed_entries(when = role, 
                  with = pkg,
                  what = details, 
                  .protect = FALSE)
```

\newpage

# Select Invited Workshops and Presentations

```{r}
xx = gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=766326727') %>% 
  mutate(Details = ifelse(is.na(Details), character(), Details)) %>% 
  tidyr::separate_longer_delim(Details, "SPLIT") %>% 
  group_by(Title) %>% 
  mutate(Details = list(as.list(Details))) %>% 
  slice(1) %>% 
  ungroup() 

ind = list()

for(i in 1:nrow(xx)){
  ind[[i]] = sum(is.na(unlist(xx$Details[[i]]))) == length(unlist(xx$Details[[i]]))
}

ind = which(unlist(ind))

for(i in 1:length(ind)){ xx$Details[[ind[i]]] = character() }

detailed_entries(xx, 
                 what  = Venue, 
                 when  = Type, 
                 with  = Title, 
                 where = Date, 
                 why   = Details,
                 .protect = TRUE)

```
