---
name: Dr. J Michael
surname: Johnson
position: 'Geographer | Data Scientist | Water Resources'
address: Fort Collins, Colorado
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD
googlescholar: MrXM9cgAAAAJ
email: 'jjohnson@lynker.com'
www: mikejohnson51.github.io
github: mikejohnson51
fontawesome: yes
docname: Curriculum Vitae
aboutme: I am a \textcolor{cyan}{\textbf{geospatial data scientist}} leading the \textcolor{cyan}{\textbf{hydrofabric development for NOAA's Next Generation National Water Model}} along with collaborative federal efforts (USGS/NOAA) to define a national suite of hydroinformatic\'s products. I seek to bridge \textcolor{cyan}{\textbf{data-intensive computational geography}} with \textcolor{cyan}{\textbf{water resources research}} to design open-source software and data solutions that ease community access to big geospatial data. I still am actively publishing research and am eager to facilitate and grow research collaborations.

headcolor: 414141
csl: apa-cv.csl
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: yes
    pandoc_args: ["--lua-filter=lua/strong.lua"]
---

```{r setup, include=FALSE}
library(scholar)
library(vitae)
library(stringr)
library(readr)
library(RefManageR)
library(tidyr)
library(dplyr)
library(gsheet)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE, error=FALSE)

gs_id = 'MrXM9cgAAAAJ'
mike_gs = get_profile(gs_id) 

cites = get_publications(gs_id) %>% 
   filter(!grepl("AGU|EGU|Meeting|meeting|Preprint|SUMMER INSTITUTE|EarthArXiv|University|Https|Universities", journal)) %>%
   filter(journal != "")

for(i in 1:nrow(cites)){
  if(!grepl("JM Johnson|J Johnson", cites$author[i])){
    cites$author[i] = get_complete_authors(id = gs_id, 
                              pubid = cites$pubid[i])
  }
}

follow = readLines('https://img.shields.io/github/followers/mikejohnson51?label=follow&style=social')
f = str_match(follow, "<title>Follow: \\s*(.*?)\\s*</title>")[,2]

stars = readLines('https://img.shields.io/github/stars/mikejohnson51?affiliations=OWNER%2CCOLLABORATOR&style=social')
s = str_match(stars, "<title>Stars: \\s*(.*?)\\s*</title>")[,2]

funds = gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=0') 

personal = sum(ifelse(is.na(parse_number(funds$amount2)), parse_number(funds$amount), parse_number(funds$amount2)))
personal = paste0("$", formatC(as.numeric(personal), format="f", digits=0, big.mark=","))

team = sum(parse_number(funds$amount))
team = paste0("$", formatC(as.numeric(team), format="f", digits=0, big.mark=","))

```

# Employment

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
  "Chief Data Scientist/ Pod Lead", "Lynker", "Fort Collins, Colorado", "Sep 2023 - Present", 
     list("Lead spatial data development for the NOAA Office of Water Prediciton",
          "Support local and state level consulting projects related to water resource managment and hazard mitigation",
          "Recruit, retain, and mentor a strong and diverse group of data scientists"
    ),
  
  "Water Resources Data Scientist", "", "", "Aug 2020 - Sep 2023", 
    character(),
  
  "Hydrofabric Technical Director", "NOAA Office of Water Prediction", "Remote", "Sep 2022 - Present", 
    list("Develop foundational geospatial products to support the Next Generation Water Modeling Framework",
         "Collaborate with the USGS to build federal software and data products to support the NOAA and USGS Water Mission Areas", 
         "Work with the CIROH member universities to support 'research to operations' hydrology",
         "Lead a team developing novel machine learning, geospatial, and cloud based solutions for open hydrologic science"),
  
  "Senior Data Scientist @ NWS / Lead Hydrofabric Developer", "", "", "Aug 2020 - Present", 
   character(),
  
   "Graduate Faculty (Affiliate)", "University of Alabama", "Remote", "Oct 2023 - Present", 
    list("Serve as member or co-chair on dissertation and thesis committees"),
  
  "Lead Data Scientist (Independent Contractor)", "Urban Flooding Open Knowledge Network", "Remote", "Nov 2019 - Apr 2023", 
    list("Co-authored successful proposals to NSF and served as an advocate for the team in the initial C-ACCEL program",
        "Developed and designed a cost effective, cloud native, building level, flood forecasting system for the Continental United States."),
  
  "Lecturer - Geography Department", "UC Santa Barbara", "Santa Barbara, California", "Summer 2020, 2021", 
    list("Designed and taught the first geoinformatics course for UC Santa Barbara."),
  
  "Research Coordinator", "NOAA Office of Water Prediction", "Tuscaloosa, Alabama", "2016", 
    list("Led students towards the successful execution of projects related to the National Water Model
Research Fellowship"),
  
  "", "Visiting Researcher", "Amsterdam, Boulder, Tuscaloosa", "2016 - 2018", 
    list("\\textbf{Institute for Environmental Studies. Vrije Universiteit}, Amsterdam, Netherlands: June - July 2019; January - March 2018", 
         "\\textbf{Research Applications Laboratory. NCAR}, Boulder, Colorado: August - September 2018",
         "\\textbf{NOAA National Water Center}. Tuscaloosa, Alabama: Summers of 2016, 2017")

) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Geography", "University of California, Santa Barbara", "Santa Barbara, CA", "2021", 
    list("\\textbf{Advisor}: Dr. Keith C. Clarke",
         "\\textbf{Committee}: Hugo Loaiciga, Kelly Caylor, David Blodgett",
         "\\textbf{Title}: The Role of Spatial Data Science in Continental Scale Hydrology: Twelve Case Studies in Data Models, Data Structures, Modeling, and Evaluation"),

  "BS in Anthropology & Geography", "California Polytechnic State University", "San Luis Obispo, CA", "2010 - 2015", 
    list("Cum Laude",
         "Outstanding Senior Award: College of Liberal Arts",
         "\\textbf{Minors}: \\textbf{(1)} GIS for Agriculture \\textbf{(2)} Water Science (Watershed Management) \\textbf{(3)} Statistics \\textbf{(4)} Economics \\textbf{(5)} Environmental Studies")
) %>% 
  detailed_entries(what = loc, 
                   when = dates, 
                   with = uni, 
                   where = degree, 
                   why = details)
```

# Publications

\textcolor{cyan}{ \href{https://tinyurl.com/mike-google-scholar}{\faicon{google} Google Scholar: `r mike_gs$total_cites` citations; \faicon{user} `r length(mike_gs$coauthors)` collaborators; \faicon{file} `r nrow(cites)` papers} \newline
\textbf{h-index} `r mike_gs$h_index`; \textbf{i-index} `r mike_gs$i10_index`}

```{r}
mutate(cites, bibtype = "article") %>% 
  as.BibEntry() %>%
  WriteBib("mike-gs.bib")

bibliography_entries("mike-gs.bib") %>%
  arrange(desc(issued))
```


# Grants and Fellowships

\textcolor{cyan}{I have personally solicited \textbf{\`r personal`} for research and development and been a core member of teams who have solicited \textbf{\`r team`}.}

```{r}
funds %>%
  mutate(amount = ifelse(is.na(amount2) | amount2 == 0,
                         amount,
                         paste0(amount, " (Subaward: ", amount2, ")"))) %>% 
  detailed_entries(what  = source, 
                   when  = date,
                   with  = name, 
                   where = amount)
```

# Teaching experience

\textcolor{cyan}{I designed an upper division spatial data science course as a UCSB Lecturer, was a teaching assistant for over 15 courses (700+ students), and have lead community workshops for national organizations.}

## \textcolor{blue}{University Teaching}

```{r}
tribble(
  ~ class, ~ uni, ~ loc, ~ dates, ~ details,
  "Introduction to Geoinformatics", "University of California, Santa Barbara, California", "Santa Barbara, CA", "2021", 
    list("Independently developed and taught to address the growing need for data science in the GIS profession.",
         "Intended to become prerequisite course for the UCSB Geography Department and Masters in GIS Curriculum",
         "\\href{https://mikejohnson51.github.io/spds/}{Open course content available here}")) %>% 
  detailed_entries(what = uni, 
                   when = dates, 
                   with = class, 
                   where = loc, 
                   why = details)
```

## \textcolor{blue}{Teaching Assistant}

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=1727236529') %>% 
  filter(type == "Teaching Assisstant")  %>%
  mutate(quarter = factor(quarter, levels = c("Fall", "Winter", "Spring", "Summer"), 
                          ordered = T),
         class_link = ifelse(is.na(link), class, 
                             paste0('<a href="',link, '">', class, '</a>'))) %>% 
  group_by(class) %>%
  mutate(points = as.numeric(year) + as.numeric(quarter)/10,
         professor = paste(unique(professor), collapse = ", ")) %>% 
  summarise(year = paste(year,collapse=', '), 
            points = max(points),
            professor = professor[1],
            division = division[1]) %>% 
  unite(data, year, sep = " ") %>% 
  arrange(desc(points)) %>% 
  detailed_entries(professor, division, class, data)
```
## \textcolor{blue}{Workshops}

```{r}
xx = gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=1176238393') %>% 
  mutate(Details = ifelse(is.na(Details), character(), Details)) %>% 
  tidyr::separate_longer_delim(Details, "SPLIT") %>% 
  group_by(Title) %>% 
  mutate(Details = list(as.list(Details))) %>% 
  slice(1) %>% 
  ungroup() 

ind = list()

for(i in 1:nrow(xx)){
  ind[[i]] = sum(is.na(unlist(xx$Details[[i]]))) == length(unlist(xx$Details[[i]]))
}

ind = which(unlist(ind))

for(i in 1:length(ind)){ xx$Details[[ind[i]]] = character() }

detailed_entries(arrange(xx, sort), 
                 what  = Venue, 
                 when  = Type, 
                 with  = Title, 
                 where = Date, 
                 why   = Details,
                 .protect = TRUE)
```

## \textcolor{blue}{Award Nominations}

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=1280463790') %>% 
  group_by(name) %>% 
  mutate(year = paste(year, collapse=', ')) %>% 
  slice(1) %>% 
  select(-sort, -source) %>% 
  detailed_entries(when = year, with = name)
```

# Open Source Software

\textcolor{cyan}{A primary output of my scientific work is open source software in personal, USGS and NOAA repositories.}
\newline
\newline
\textcolor{cyan}{\href{https://github.com/mikejohnson51}{\faicon{github} Github: \faicon{user} `r f` followers; \faicon{star} `r s` stars}}

```{r}
tribble(
  ~ pkg, ~ role, ~ details,
  "\\href{https://github.com/mikejohnson51/AOI}{AOI}", "Lead Developer", "Fast and flexible geocoding and AOI creation.",
  "\\href{https://github.com/mikejohnson51/climateR}{climateR}", "Lead developer", "Instant access to gridded and observation climate data.",

  "\\href{https://github.com/mikejohnson51/climateR-catalogs}{climateR-catalogs}", "Lead developer", "A consistent federated data catalog for programmatic access.",

  "\\href{https://github.com/mikejohnson51/zonal}{zonal}", "Lead developer", "Fast, flexable spatial data summarization.",

  "\\href{https://github.com/mikejohnson51/nwmTools}{nwmTools}",  "Lead developer", "National Water Model Streamflow access.",

  "\\href{https://github.com/doi-usgs/nhdplusTools}{DOI-USGS/nhdplusTools}",  "Author", "Manipulating hydrographic data with the NHDPlus data model.",

  "\\href{https://github.com/doi-usgs/dataRetrieval}{DOI-USGS/dataRetrieval}",  "Author", "R Interface to the USGS data holdings.",

  "\\href{https://github.com/doi-usg/hyRefactor}{DOI-USGS/hyRefactor}",  "Author", "Manipulating the NHDPlus Network for Hydrologic Modeling.",

  "\\href{https://github.com/NOAA-OWP/hydrofabricI}{NOAA-OWP/hydrofabric}", "Lead Developer", "Generating data products for continental scale hydrology",
   "\\href{https://github.com/mikejohnson51/AHGestimation}{AHGestimation}", "Lead Developer", "Estimating robust, mass conserving AHG relationships with cross section hydrualics and geometry",
) %>%
 detailed_entries(when = role, 
                  with = pkg,
                  what = details, 
                  .protect = FALSE)
```

# Invited Presentations

```{r}
xx = gsheet2tbl('https://docs.google.com/spreadsheets/d/1Zyyk8laciZ-3oAJl_tGGLeRcpfuUJpTRtTio0gMO06o/edit#gid=766326727') %>% 
  mutate(Details = ifelse(is.na(Details), character(), Details)) %>% 
  tidyr::separate_longer_delim(Details, "SPLIT") %>% 
  group_by(Title) %>% 
  mutate(Details = list(as.list(Details))) %>% 
  slice(1) %>% 
  ungroup() 

ind = list()

for(i in 1:nrow(xx)){
  ind[[i]] = sum(is.na(unlist(xx$Details[[i]]))) == length(unlist(xx$Details[[i]]))
}

ind = which(unlist(ind))

for(i in 1:length(ind)){ xx$Details[[ind[i]]] = character() }

detailed_entries(arrange(xx, sort), 
                 what  = Venue, 
                 when  = Type, 
                 with  = Title, 
                 where = Date, 
                 why   = Details,
                 .protect = TRUE)

```
